\documentclass[letterpaper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks=true,
    pdfborder={1 1 1},
    linkcolor=black, citecolor=black, urlcolor=black]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\normalsize{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\normalsize{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\begin{document}
% ---- TOP
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Joshua Murray\vspace{5pt}}} & \\
  Lamont-Doherty Earth Observatory, Columbia University & \today \\ 
  61 Rte 9W &\\
  Palisades, NY & Phone: +1 (609)356-9088  \\ 
  10964 &  Email: \href{mailto:}{joshmurr@mit.edu}
\end{tabular*}

% ---- EDUCATION
\vspace{5pt}
\section{~~Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Columbia University}{New York, NY}
      {Postdoctoral Research Scientist\vspace{5pt}}{September 2024}
      {\scriptsize \textit{ \small{\newline{}\textbf{Lamont-Doherty Earth Observatory} ~~~With Prof. Peter Kelemen}}}
    \resumeSubheading
      {Massachusetts Institute of Technology}{Cambridge, MA}
      {PhD\vspace{5pt}}{August 2024}
      {\scriptsize \textit{ \small{\newline{}\textbf{Earth, Atmospheric and Planetary Sciences} ~~~With Prof. Oli Jagoutz}}}
    \resumeSubheading
      {Princeton University}{Princeton, NJ}
      {A.B.\vspace{5pt}}{June 2018}
      {\scriptsize \textit{ \small{\newline{}\textbf{Concentration in Geosciences. Certificate in Applications of Computing}}}}

    \resumeSubHeadingListEnd

\vspace{3pt}
\section{~~Publications}
  \resumeSubHeadingListStart
    \resumeItem
    {Sedimentary constraints on silicate weathering during the Taconic orogeny in Newfoundland}
    {\\Joshua Murray, Oliver Jagoutz, Kristin Bergmann.~~~ \textit{In prep}}
    \resumeItem
    {Olivine alteration and the loss of Mars' early carbon}{\\Joshua Murray, Oliver Jagoutz.~~~ \textit{In press, Science Advances}}
    \resumeItem
    {\href{https://doi.org/10.1038/s41561-023-01342-9}{Palaeozoic cooling modulated by ophiolite weathering through organic carbon preservation}}{\\Joshua Murray, Oliver Jagoutz.~~~ \textit{Nature Geoscience} (2023)}
    \resumeItem
    {\href{https://doi.org/10.1016/j.epsl.2023.118269}{Eruption history of the Columbia River Basalt Group constrained by high-precision U-Pb and $^{40}$Ar/$^{39}$Ar\\ geochronology}}{\\Jennifer Kasbohm, Blair Schoene, Darren Mark, \textbf{Joshua Murray}, Stephen Reidel, Dawid Szymanowski, Dan Barfod,\\ Tiffany Barry.~~~ \textit{Earth and Planetary Science Letters, 617, 118269} (2023)}
\resumeSubHeadingListEnd

\vspace{3pt}
\section{~~Talks and Presentations}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Invited: Ultramafic weathering and the carbon cycle of Earth and Mars}{}
    {Princeton University Solid Earth Brown Bag - April 2024}{} 
    \resumeSubheading
    {Invited: Glaciations induced by ophiolite weathering through clay formation}{}
    {Stanford University Earth \& planetary science seminar - February 2024}{} 
    \resumeSubheading
    {Invited: Ophiolite obduction and clay formation as a driver of Paleozoic glaciations}{}
    {Brown University geochemistry, mineralogy, and petrology seminar - Fall 2023}{} 
    % \resumeSubheading
    % {Ophiolite weathering, clay formation, and Earth's Paleozoic glaciations}{}
    % {Bates College Department Lecture Series - Fall 2023}{} 
    \resumeSubheading
    {Increased organic carbon burial through ophiolite obduction}{}
    {NSF-FRES Climate-tectonics workshop 2023 - Talk}{}  
   \resumeSubheading
    {A sedimentary sink for Mars' early carbon}{}
    {AGU Fall Meeting 2022 - Talk}{}  
  \resumeSubheading
    {Ophiolite-derived clays enhance organic carbon burial}{}
    {AGU Fall Meeting 2022 - Poster}{}
  \resumeSubheading
    {The natural levers of Earth's long-term climate}{}
    {New England Aquarium Carlson lecture 2022 - Poster}{}
  \resumeSubheading
    {Silicate weathering products of mafic and ultramafic rocks as a control on steady state climate}{}
    {AGU Fall Meeting 2021 - Talk}{}
\resumeSubHeadingListEnd
    
\vspace{3pt}
\section{~~Honours and Awards}
  \resumeSubHeadingListStart
  \resumeSubheading
    {MIT EAPS Award for Excellence in Teaching}{2021}
    {Awarded to teaching assistants `who have met the highest levels of performance'}{}    
   \resumeSubheading
    {MIT Presidential Fellowship}{2018-2019}
    {Funds tuition and living costs for the first academic year at MIT}{}    
  \resumeSubheading
    {William Bonini '48 Teaching Award}{2018}
    {Awarded to Princeton Geosciences Senior for commitment to teaching}{}
  \resumeSubheading
    {Smith-Newton Environmental Scholar}{2016-2018}
    {Research funding and support from the High Meadows Environmental Institute}{}  
  \resumeSubheading
    {Fulbright Sutton Trust US Programme}{2012-2014}
    {Supports first-generation, low-income UK state school students in attending university in the US}{}
    \resumeSubHeadingListEnd
    
\vspace{3pt}
\section{~~Teaching Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
    {MIT 12.116 - Analysis of Geologic Data}{Spring 2024}
    {TA. Lead digitization of field maps. Work through cross sections, stratigraphic columns, final report etc.}{} 
    \resumeSubheading
    {MIT 12.115/12.482 - Field Geology}{January 2024}
    {TA. Organised 3-week trip to Muddy Mountains, NV. Instructed mapping techniques, paper and digital.}{} 
    \resumeSubheading
    {MIT 12.001 - Introduction to Geology}{Fall 2020, Fall 2022}
    {TA. Organised Western MA trip. Led labs and some lectures. Wrote exam questions. Graded.}{} 
    \resumeSubheading
    {MIT 12.S597 - Seminar on Teaching in Earth Science}{January 2022}
    {Participant in seminar on pedagogical concepts \& strategies for teaching equitably, course design, feedback.}{}
  \resumeSubheading
    {Princeton GEO 370 - Sedimentology}{Spring 2018}
    {TA. Organised trip to Shark Bay, Australia. Assisted problem sets.}{} 
  \resumeSubheading
    {Princeton GEO 373 - Structural Geology}{Fall 2017}
    {Field TA. Helped students with mapping and observation in Southern California.}{} 
    \resumeSubHeadingListEnd


\vspace{3pt}
\section{~~Languanges and Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Coding}{MATLAB, Java, HTML, R}
    \resumeSubItem{Adobe}{Illustrator, Photoshop, Premiere, InDesign}
    \resumeSubItem{Mapping}{GIS, MATLAB Mapping Toolbox, Paper \& pencil}
    \resumeSubItem{Driving}{Automatic, Manual, Field vehicles etc.}
    \resumeSubItem{Laboratory}{Mineral separation, Petrographic microscope, Mineral dissolution}
    \resumeSubItem{Interests}{Film photography, ultimate (frisbee), cooking and baking}
    \resumeSubHeadingListEnd
    
\vspace{3pt}
\section{~~Mentoring and Service}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Reviewer}{2024}
    {Proceedings of the National Academy of Sciences; Journal of Geophysical Research}{}
    \resumeSubheading
    {COG3 Seminar Organiser}{2022-2023}
    {One of two organisers of MIT's seminar in Chemical Oceanography, Geology, Geochemistry, and Geobiology}{}  
    \resumeSubheading
    {President - EAPS Student Advisory Committee (ESAC)}{~~~~~~~~~~~~~~~~~~2020-2021}
    {Liaise with students and leadership to build meaningful community through events and dialogue}{}  
  \resumeSubheading
    {Mentor - Fulbright Sutton Trust US Programme Mentor}{~~~~~~~~~2019-}
    {Mentored two first-generation British students each year through US university and financial aid apps}{}
\resumeSubheading
    {Assistant Coach - MIT Men's Ultimate}{~~~~~~~~~~~~~~~~~~~~2019-2024}
    {Lead practices, logistics, and strategy over short-term (tournaments) and long-term (seasons)}{}  
  \resumeSubheading
    {Mathey College RCA of the Year}{~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~2017-2018}
    {Acknowledged for my work building community within the residential college system}{}  
    \resumeSubheading
    {President - Princeton Undergraduate Geologic Society (PUGS)}{~~~~~~~~~~~~~~~~~~~~~~~~~~~~~2017-2018}
    {Organised community building events and a 40 person department field trip  to Scotland}{}  
\resumeSubHeadingListEnd


\vspace{3pt}
\section{~~Field Experience}
  \resumeSubHeadingListStart
    \resumeSubItem{Isle of Arran, Scotland}{1 week, November 2013}
    \resumeSubItem{Owens Valley, CA}{1 week, March 2015}
    \resumeSubItem{Columbia River Basalt}{11 weeks total. Summer 2015, 2016, 2017}
    \resumeSubItem{Orocopia Mountains, CA}{3 weeks total, October 2015, 2017}
    \resumeSubItem{Andros Island, Bahamas}{2 weeks, March 2016}
    \resumeSubItem{Iceland}{1 week, Summer 2016}
    \resumeSubItem{Altiplano, Bolivia}{4 weeks, Summer 2016}
    \resumeSubItem{Shark Bay, Australia}{2 weeks, March 2018}
    \resumeSubItem{Western Scotland}{1 week, May 2018}
    \resumeSubItem{Piute Mountains, CA}{3 weeks, January 2020}
    \resumeSubItem{White Mountains, NH}{1 week, April 2021}
    \resumeSubItem{Newfoundland, Canada}{2 weeks, November 2021}
    \resumeSubItem{Muddy Mountains, Nevada}{3 weeks, January 2024}
    \resumeSubHeadingListEnd
\end{document}